Localisation and Sensor Privacy Using the Extended Information Filter and Secure Weighted Aggregation\thanksref{footnoteinfo}

### 2020-08-21 main.tex
Couple small things

The formal security game for IND-CPA has been given in Appendix \ref{app:ind-cpa}.
\end{definition}
Private aggregation schemes aim for the security notion of Aggregator Obliviousness (AO) \cite{}. 
\begin{definition}
An encryption scheme meets AO security if no colluding subset of participants \textit{excluding} the aggregator gains additional information about the remaining aggregation values given only their encryptions, while any colluding subset \textit{including} the aggregator learns only their sum.

@@

% Each appendix must have a short title.
% Sections and subsections are supported
% in the appendices.
\appendix
\section{Indistinguishability under the Chosen Plaintext Attack (IND-CPA)} \label{app:ind-cpa}
\section{Aggregator Obliviousness (AO)} \label{app:ao}

>>>>

The formal security game for IND-CPA has been given in Appendix \ref{app:ind_cpa}.
\end{definition}
Private aggregation schemes aim for the security notion of Aggregator Obliviousness (AO) \cite{}. 
\begin{definition}
An encryption scheme meets AO security if no colluding subset of participants \textit{excluding} the aggregator gains additional information about the remaining aggregation values given only their encryptions, while any colluding subset \textit{including} the aggregator learns only their sum.

@@

% Each appendix must have a short title.
% Sections and subsections are supported
% in the appendices.
\appendix
\section{Indistinguishability under Chosen Plaintext Attack (IND-CPA)} \label{app:ind_cpa}
\section{Aggregator Obliviousness (AO)} \label{app:ao}
